Using Scipion for Stream Image Processing at Cryo-EM Facilities

### 2018-04-19 3.workflow_scilifelab.tex
from home Marta (swedden) comments
Stefan

\subsubsection{Network Setup and IT Infrastructure}
At the heart of the \scilifelab computational infrastructure there is a storage and pre-processing server (the staging server). This machine has roughly 200 TB of storage (4 ZFS RAIDZ2 pools with 11 HDDs each), 2 NVIDIA GeForce GTX 1070 GPUs, 2 Intel Xeon E5-2630v4 CPUs (10 cores, 2.2 GHz, HT), 384 GB RAM, and a dual-port 10 GbE network card. The storage pool is exported via NFS and Samba, so the microscope computers can write data there directly and other machines can access it.
%Unfortunately, the K2 [** Jose Miguel, what is K2?, do you have 2 cameras? in the same microscope or in different ones, this is confusing, comment when ] computer writes data to a local SSD RAID while the Falcon-III does it to a dedicated storage server. %, in order to avoid interruption of data collection due to network issues.

In order to avoid interruption of data collection due to network issues each microscope has its own dedicated storage, that in the case of the Titan microscope is double since it may be connected to two different cameras, a K2 and a Falcon III.  In this way, after starting the data collection, users launch a script that continuously moves the produced data from the adequate storage to the staging server.

%ata on the staging server, in an organized folder structure, we
%can run pre-processing directly on the server.] If data processing is started soon
%after data collection the incoming data file should be in RAM-cache and  no
%disk access in needed, which is important with performance in mind. 
After processing, users may  copy their data to external USB drives from two workstations in the microscope room that have access to the storage pool via NFS.
There is also a dedicated download server which have access to the NFS export. This download server can be reached though the Internet and allow downloads via rsync (over SSH) or SFTP.

All these computers are connected to a 10 GbE network switch. This is a private
network without external access. The only machine accessible from the Internet
is the data download server, which has a dual-port 10 GbE network adapter (one
used for the private network, one for the external network). %Both the K2 computer and the Falcon-III dedicated storage server had one unused 10GbE interface that could be used to connect them to our private network, without having to interfere with the default setup.

\subsubsection{Additional Software Developments: \emph{Session Wizard}}
In order to interface \scipion with the microscope infrastructure an upgraded version of the original script developed at the CNB was used. Unfortunately, it was difficult to reuse the existing code due to a different folder structure and, more important, a different logic about users and microscopes management. %To address the new set of requirements, a new wizard is under development at \scilifelab. For this new wizard, a basic data model was designed representing the current processing and data organization at \scilifelab. %The model is composed by the following entities:

@@

When a user starts a data collection, the wizard is also executed using the command \textit{session-titan} (or \textit{session-talos}). The wizard will fetch the reservations for this day using the webservice API provided by \emph{Booked Scheduler} and will check which user is operating the microscope. From the reservation information, the wizard will also detect if it is an internal or a national facility project. If the latter, more information will be retrieved from the Application Portal (such as principal investigator, project code, contact person or invoice address). After gathering all this information, the wizard will store this information, create the processing environment and launch \scipion. %For example, the movies-import protocol will already point to the location where the files will be written for this session. Moreover, taking into account which microscope-camera is being  used, the files pattern can be inferred.

The current implementation of the wizard stores each session in a simple database file. This database, together with extra information from the Booking System and the Application Portal, is used to generate reports for a given period and the associated invoices. %The generation of a session report is under development, that will provide a summary and useful information for users to access the acquired data. 
%[** this last sentence is not very informative]

The described session wizard can be found at  \url{https://github.com/delarosatrevin/scipion-session}. It has been design to satisfy \scilifelab requirements and, although readers are welcomed to try it, no support is offered.

>>>>

\subsubsection{Network Setup and IT Infrastructure}
At the heart of cryo-EM National Facility computational infrastructure there is a storage and pre-processing server (the staging server). This machine has roughly 200 TB of storage (4 ZFS RAIDZ2 pools with 11 HDDs each), 2 NVIDIA GeForce GTX 1070 GPUs, 2 Intel Xeon E5-2630v4 CPUs (10 cores, 2.2 GHz, HT), 384 GB RAM, and a dual-port 10 GbE network card. The storage pool is exported via NFS and Samba, so the microscope computers can write data there directly and other machines can access it.
%Unfortunately, the K2 [** Jose Miguel, what is K2?, do you have 2 cameras? in the same microscope or in different ones, this is confusing, comment when ] computer writes data to a local SSD RAID while the Falcon-III does it to a dedicated storage server. %, in order to avoid interruption of data collection due to network issues.

In order to avoid interruption of data collection due to network issues each microscope has its own dedicated storage, that in the case of the Titan microscope is double since it may be connected to two different cameras, a K2 and a Falcon III. Hence an script to continuously move the produced data from the adequate storage to the staging server has been created.

%In this way, after starting the data collection, users launch a script that continuously moves the produced data from the adequate storage to the staging server.

%ata on the staging server, in an organized folder structure, we
%can run pre-processing directly on the server.] If data processing is started soon
%after data collection the incoming data file should be in RAM-cache and  no
%disk access in needed, which is important with performance in mind. 
After processing, users may  copy their data to external USB drives from two workstations in the microscope room that have access to the storage pool via NFS.
There is also a dedicated download server which has access to the NFS export. This download server is accessible from  the Internet and allow downloads via rsync (over SSH) or SFTP.

All these computers are connected to a 10 GbE network switch. The only machine accessible from the Internet is the data download server, which has a dual-port 10 GbE network adapter (one used for the internal network, one for the external network). %Both the K2 computer and the Falcon-III dedicated storage server had one unused 10GbE interface that could be used to connect them to our private network, without having to interfere with the default setup.

\subsubsection{Additional Software Developments: \emph{Session Wizard}}
In order to interface \scipion with the microscope infrastructure an upgraded version of the original script developed at CNB was used. Unfortunately, it was difficult to reuse the existing code due to a different folder structure and, more important, a different approach to user and microscope management. %To address the new set of requirements, a new wizard is under development at \scilifelab. For this new wizard, a basic data model was designed representing the current processing and data organization at \scilifelab. %The model is composed by the following entities:

@@

When a user starts a data collection, the wizard is executed using the command \textit{session-titan} (or \textit{session-talos}). The wizard determines which user has booked the microscope by fetching today's booking information from \emph{Booked Scheduler} through their web API. From the reservation information the wizard will also detect if it is an internal or a national facility project. 
In case of the latter, additional information will be retrieved from the Application Portal (such as principal investigator, project code, contact person or invoice address). After gathering all this information the wizard will store it, create the processing environment and launch \scipion. %For example, the movies-import protocol will already point to the location where the files will be written for this session. Moreover, taking into account which microscope-camera is being  used, the files pattern can be inferred.

The current implementation of the wizard stores each session in a simple database file. This database, together with extra information from the Booking System and the Application Portal, is used to generate invoices and reports for a given period. %The generation of a session report is under development, that will provide a summary and useful information for users to access the acquired data. 
%[** this last sentence is not very informative]

The described session wizard can be found at  \url{https://github.com/delarosatrevin/scipion-session}. It has been designed to satisfy the requirements for \scilifelab and, although readers are welcomed to try it, no support is offered.  \emph{Booked Scheduler} is available at (\url{https://www.bookedscheduler.com/})
